---
title: "gren: Group-regularized logistic elastic net regression"
author: 
  name: "Magnus Münch"
  affiliation: 
    1. Department of Epidemiology & Biostatistics, VU University Medical Center, Amsterdam, The Netherlands
    2. Mathematical Institute, Leiden University, Leiden, The Netherlands
  email: m.munch@vumc.nl
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{gren: Group-regularized logistic elastic net regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

The package enables the user to enhance classification performance and variable selection of the logistic elastic net through the inclusion of external information. The information comes in the form of a partitioning of the features into non-overlapping group. Example of such co-data are:

1. Response-independent summaries in the primary data (e.g. standard deviation).
2. Feature-specific summaries from an independent study (e.g. p-values). 
2. Feature groupings from public data bases (e.g. pathways). 

## Elements of the package

Key elements of the <code>gren</code> package are:

1. The main function of the package is conveniently named <code>gren</code>.
2. A convience function that cross-validation predictions is included as <code>cv.gren</code>

## Getting started

The <code>gren</code> package is available online. Installation from Github is as follows:

```{r, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("magnusmunch/gren", force=TRUE)
```

Note that if <code>devtools</code> is already installed, the first line may be skipped. The <code>gren</code> package depends on these following R packages: <code>glmnet</code>, <code>Rcpp</code>, and <code>pROC</code>.

# Example 1: microRNA data
